Demystifying the Computer Science \\PhD Admission in US Universities\\{\large A guide for Vietnamese and International Students

### 2023-06-12 phd-cs-us.tex
updates

\subsection{What can you do to increase your admission chance?}
 Show something that makes you \textbf{stand out}, e.g., are you a female or a minority in CS (research for this on Google)? Do you participate in outreach activities that help increase diversity and inclusion in CS?  All of these are important in CS in the US.

>>>>

\subsection{What can you do to increase your admission chance?}

 Show something that makes you \textbf{stand out}, e.g., are you a female or a minority in CS (research for this on Google)? Do you participate in outreach activities that help increase diversity and inclusion in CS?  All of these are important in CS in the US.
